SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-16 scipy-1.0/paper.tex
ENH: intro: commented out LIGO sentence in first paragraph "For example" is not precisely appropriate here because the LIGO is not an example of SciPy _providing_ building blocks but of a project making use of them. It is a strong example and belongs somewhere around here... just not quite here.

SciPy is a library of numerical routines for the Python programming
language that provides fundamental building blocks for modeling and
solving scientific problems.  For example, when LIGO, the Laser
Interferometer Gravitational-Wave Observatory, recently announced the
discovery of gravitational waves, their published Python analysis
scripts\cite{LIGO-open,alex_nitz_2018_1596771,GW150914-Python,
PhysRevD.93.122003} imported many different SciPy submodules for:
signal processing, interpolation, input / output, optimization, statistics,
integration, and more. SciPy has routines for solving
classes of generic problems such as optimization, integration,
interpolation, eigenvalues, and linear systems.  It also provides
specialized data structures, such as sparse arrays and k-dimensional
trees. SciPy is built on top of NumPy\cite{vanderwalt2011numpy,Oliphant-2015},
which provides array data structures and related fast numerical routines.
SciPy is itself the foundation upon which higher level scientific libraries,
including scikit-learn\cite{pedregosa2011scikit}
and scikit-image\cite{vanderwalt2014scikit}, are built.

>>>>

SciPy is a library of numerical routines for the Python programming
language that provides fundamental building blocks for modeling and
solving scientific problems. 
// For example, when LIGO, the Laser
Interferometer Gravitational-Wave Observatory, recently announced the
discovery of gravitational waves, their published Python analysis
scripts\cite{LIGO-open,alex_nitz_2018_1596771,GW150914-Python,
PhysRevD.93.122003} imported many different SciPy submodules for:
signal processing, interpolation, input / output, optimization, statistics,
integration, and more.
SciPy has routines for solving
classes of generic problems such as optimization, integration,
interpolation, eigenvalues, and linear systems.  It also provides
specialized data structures, such as sparse arrays and k-dimensional
trees. SciPy is built on top of NumPy\cite{vanderwalt2011numpy,Oliphant-2015},
which provides array data structures and related fast numerical routines.
SciPy is itself the foundation upon which higher level scientific libraries,
including scikit-learn\cite{pedregosa2011scikit}
and scikit-image\cite{vanderwalt2014scikit}, are built.
